---
title: "Fish Length Assignment"
author: "Paloma Cartwright"
date: "02/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## This is the main header of the page

*My name is **Paloma**.*

I want to write this^2^ as a superscript and this~word~ as a subscript.

I want to make a list of fruits.

Fruit types

    -   Apples

        -   Green Apples

        -   Red Apples

    -   Bananas

    -   Grapes

        -   Green Grapes

        -   Purple Grapes
        

Fruit Types 

    1. Apples 
    2. Bananas
    

I removed the picture I had inserted here because it was of my goddaughter. Now I added another note because I forgot to usethis::use_github() so it never actually went to github. This is now my change so I can commit and pull and push again. 
```{r}
standard_weight <- function(a, b, length){
  a*(length^b)
}

print(Milkfish <- standard_weight(a=0.0905, b=2.52, length=60))
print(Giant_Trevally <- standard_weight( a = 0.0353, b = 3.05, length = 60))
print(Giant_Barracuda <- standard_weight(a = 0.0181, b = 3.27, length = 60))

fish_length <- seq(from = 0, to = 200, by = 1)

Giant_Barry <- standard_weight(a = 0.0181, b = 3.27, length = fish_length)

barracuda_df <- data.frame(fish_length, Giant_Barry)

ggplot(data = barracuda_df, aes(x = fish_length, y = Giant_Barry)) + 
         geom_point() +
         labs(x = "Fish Length(cm)", 
              y = "Barracuda Weight(g)", 
              title = "Barracuda Weight by Increasing Lengths")


```

